---
title: "Replicating Liu et al"
author: "Jon Page"
date: "16/06/2020"
Last Updated: date()
output: github_document
---

This notebook is to document my replication of Liu et al's model from their 2019 paper.

I have downloaded the model code from github (https://github.com/yliu11/NEE_Bayes_model, accessed 15/06/20).

I need to coerce data into the required input formats and produce a wrapper script.

Let's activate!

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())
```

## Working on Walnut Gulch

I will first attempt to replicate the modelling at one site, Walnut Gulch (FluxNet SiteID US_Wkg).

```{r Site Selection, include=FALSE}
Site = "US-Wkg"
```

I need to access the full fluxnet data for this, as the data I have from previous modelling of this site does not include SWC. Daily FluxNet data will be used.


```{r Liu Input Data}
if (file.exists(paste0(Site,"_LiuInput.Rdata"))){
  message("Gosh! Processed daily FluxNet data already exists for ",Site)
} else {
  source("FluxNetProcess.R")
  FluxNetProcess(Site)
}
```

